{\LARGE {\color{red}PLACEHOLDER-TITLE:} Functional Linear Regression in a Scalar-on-Function Setting with Applications to SOMETHING}

### 2021-10-31 main.tex
Increment

   In practice, this results in a large and often difficult to solve system of equations. Even if solved, the result is often a noisy function $\beta(\dot{•})$ that is not useful for interpretation since it does not utilize the intuition of smooth functions. Another reason why estimation is not feasible using this approach is colinearity. \\

   If we approximate the scalar-on-functional regression as
  	\begin{equation}
     Y_i = \sum_{j = 1}^{n} \beta(t_{j})X_i(t_{j}) + \epsilon_{j}
    \end{equation}, it becomes clear that if $t_{j}$ is close to $t_{j'}$, $X_{i}(t_{j})$ is close to $X_{i}(t_{j'})$ there will be vectors $X_{i} = (X_i(t_1), \dots, X_i(t_J))'$ that are highly correlated and thus lead to large variances. {\color{red} isn't something missing here? Like "and employ standard multivariate linear regression"}

>>>>

   In practice, this results in a large and often difficult to solve system of equations. Even if solved, the result is often a noisy function $\hat{\beta}(s)$ that is not useful for interpretation since it does not use the intuition of smooth functions. Another reason why estimation is not feasible using this approach is colinearity.
   If we approximate the scalar-on-functional regression by assuming a set of discrete observation points for all realizations of the data generating process as
  	\begin{equation}
     Y_i = \sum_{j = 1}^{n} \beta(t_{j})X_i(t_{j}) + \epsilon_{j}
    \end{equation}, it becomes clear that if $t_{j}$ is close to $t_{j'}$, $X_{i}(t_{j})$ is close to $X_{i}(t_{j'})$ there will be vectors $X_{i} = (X_i(t_1), \dots, X_i(t_J))'$ that are highly correlated and thus lead to large variances. {\color{red} isn't something missing here? Like "and employ standard multivariate linear regression"}
